

SHit to be done:
1. outlier treatment - idk
2. Graphs for Bivariate analsis and heatmap
3. 
```{r}
library(base)
library(ggplot2)
library(grid)
```


```{r}
data <- `Resort01.(1)`
str(data)

head(data)
View(data)
```


```{r}
which(is.na(data))
col <- as.list(colnames(data))
for (i in col)
{
  #cat("No null values in: ", i)
  if(!(identical(which(is.na(data$i)), character(0))))
    {
    print(i)
    print(" ,Has no null values\n")
    }
}

if(!all(data$LeadTime > 0)){
  print('ALl values greater than 0')
}
print(data[data$LeadTime < 0,])
print(all(data$LeadTime) < 0 )

for (i in col){
  print(i)
  cat(table(with(data, data[,i] < 0)))
}


```

```{r}
summary(data)
```


```{r}
for (i in col){
  uni <- as.list(unique(data[,i]))
    cat("\nUnique values in",i, "are:  \n", unique(data[,i])) #should only print the first 10 values 
}
```
```{r}
numeric <- c("LeadTime", "StaysInWeekendNights", "StaysInWeekNights", "Adults", "PreviousCancellations", "PreviousBookingsNotCanceled", "BookingChanges")

categorical <- c("IsCanceled", "Children", "Babies", "Meal", "Country", "MarketSegment", "IsRepeatedGuest", "ReservedRoomType" , "AssignedRoomType", "DepositType", "CustomerType", "RequiredCarParkingSpaces", "TotalOfSpecialRequests")

for (i in categorical){
  data[,i] <- as.factor(data[,i])
}
summary(data)
class(data$IsCanceled)
```

```{r}
histogram_boxplot <- function(arg1){
  p2 <- ggplot(data, aes(x = arg1)) + geom_histogram(color = 'black', fill = 'white') + geom_vline(aes(xintercept=mean(arg1)), color="blue", linetype="dashed", size=1) + ggtitle(cat("Histogram for "))
  p1 <- ggplot(data, aes(y = arg1)) + geom_boxplot() + coord_flip()
  grid.newpage()
  return(grid.draw(rbind(ggplotGrob(p1), ggplotGrob(p2), size = "last")))
} #add x-ylabels and title #add mean for the boxplot if possible like a blue line or star

for (i in numeric){
  print(histogram_boxplot(data[,i]))
}
```

```{r}
to_be_transformed = c("LeadTime")
for (i in to_be_transformed){
  data[,i] <- log(data[,i])
}

for (i in numeric){
  print(histogram_boxplot(data[,i]))
}
```



ggplot(data, aes(y = LeadTime)) + geom_boxplot() + coord_flip()
par(new = TRUE)

p2 <- ggplot(data, aes(x = StaysInWeekendNights)) + geom_histogram(color = 'black', fill = 'white') + geom_vline(aes(xintercept=mean(StaysInWeekendNights)),
                                                                                                                 color="blue", linetype="dashed", size=1)
p1 <- ggplot(data, aes(y = StaysInWeekendNights)) + geom_boxplot() + coord_flip()
grid.newpage()
grid.draw(rbind(ggplotGrob(p1), ggplotGrob(p2), size = "last"))


histogram_boxplot(data$LeadTime)#outliers
histogram_boxplot(data$StaysInWeekendNights)#needs ot be scaled
histogram_boxplot(data[,numeric[3]])#needs to be scaled
histogram_boxplot(data$Adults)#needs to be scaled, outliers
histogram_boxplot(data$PreviousCancellations)#needs to be scaled,outliers
histogram_boxplot(data$PreviousBookingsNotCanceled)#needs to be scaled, outliers
histogram_boxplot(data$BookingChanges)#needs to be scaled, outliers


for (i in numeric){
  histogram_boxplot(data[,i])
}
I

barplots <- function(arg1){
  ggplot(data, aes(x = arg1)) + geom_bar(fill = 'blue')
}
barplots(data$IsCanceled)
barplots(data$Children)


#Bivariate analysis 

```{r}
nums <- unlist(lapply(data, is.numeric))  
data[,nums]
correlation <- round(cor(data[,nums]),2)
correlation

cancelled <- subset(data, IsCanceled == 0)
not_cancelled <- subset(data, IsCanceled == 1)

library(reshape2)
melted_cormat <- melt(correlation)
head(melted_cormat)

ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile() + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```



#Barplots of every categorical data against IsCancelled

```{r}
for (i in categorical){
  
  print(ggplot(data, aes(x = IsCanceled, y = i)) + geom_boxplot())
  
}
ggplot(data = data, aes(x = IsCanceled, y = LeadTime )) + geom_bar(stat="identity",fill="steelblue") + geom_text(aes(label=length(IsCanceled)), vjust=-0.3, size=3.5)+ theme_minimal()
length(data[data$IsCanceled == 0,])

percentage_a = dim(data[data$IsCanceled == 0,])[1]/dim(data)[1] * 100
percentage_b = dim(data[data$IsCanceled == 1,])[1]/dim(data)[1] * 100
percentage_a
percentage_b
dim(data)[1]
```

```{r}
library(gapminder)
for (i in numeric){
  print((noquote(i)))
  print(ggplot(data, aes(x = IsCanceled, y = noquote(i))) + geom_boxplot())
  
}
ggplot(data, aes(x = IsCanceled, y = LeadTime)) + geom_boxplot() + 
              stat_summary(fun.y = mean, geom = "errorbar", 
               aes(ymax = ..y.., ymin = ..y..),
               width = .75, linetype = "dashed")
```

